PLFS Policy Regarding Writes by Others

### 2010-10-05 design_choices/other_writes/plfs_other_write.tex
git-svn-id: https://plfs.svn.sourceforge.net/svnroot/plfs/doc@347 979fb63a-54b4-4514-8d67-9ab8ea1b59df

The third approach, and the approach taken by Version 1.0.0, is for all
\droppings\ to always be created with full permissions (\ie\ ({\\tt
 (S\_IRWXU|S\_IRWXG|S\_IRWXO)}) which allows A to easily remove any 
\droppings\ created by B.  We then attempt to limit permissions by
setting the permissions of all directories within the \container\ 
appropriately.  The drawback of this approach is that if A gives B read
permissions on the file, then the \droppings\ will be globally writable
and the directories will allow B read access.  Therefore B cannot 
create new droppings but can overwrite and truncate existing droppings.
We explicitly check for this and prevent this for access through \fuse,
but this does allow B unauthorized access through the \store.

Given these constraints and our desire to make a filesystem conforming
the most closely to user expectations and given the lack of obvious
visibility to the \store, we have currently chosen to use the third
approach in Version 1.0.0.  This allows write by others and allows
the original owner full access to their files after write by others
without any intermediate steps such as {\tt chmod()} or {\tt chown()}.
This does allow unauthorized overwriting on the \store\ when an other
has only read access.

>>>>

The third approach, and the approach taken by Version 1.0.0, is for all
\droppings\ to always be created with full permissions (\ie\ ({\\tt
 (S\_IRWXU|S\_IRWXG|S\_IRWXO)}) which allows A to easily remove any 
\droppings\ created by B.  We then attempt to limit permissions by
setting the permissions of all directories within the \container\ 
appropriately.  The drawback of this approach is that if A gives B read
permissions on the file, then the \droppings\ will be globally writable
and the directories will allow B read access.  Therefore B cannot 
create new droppings but can overwrite and truncate existing droppings.
We explicitly check for this and prevent this for access through \fuse,
but this does allow B unauthorized access through the \store.  However,
given how we implement {\tt chmod()} and {\tt chown()} as described
above, user A can {\tt chmod()} and {\tt chown()} the file and this
will close the hole on the \store.

Given these constraints and our desire to make a filesystem conforming the most
closely to user expectations and given the lack of obvious visibility to the
\store, we have currently chosen to use the third approach in Version 1.0.0.
This allows write by others and allows the original owner full access to their
files after write by others without any intermediate steps such as {\tt
chmod()} or {\tt chown()}.  This does allow unauthorized overwriting on the
\store\ when an other has only read access but only until the owner does a {\tt
chmod()} or {\tt chown()}.
